\documentclass[12pt]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[utf]{kotex}
\usepackage{hyperref}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=1
}

\lstset{style=mystyle}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.4pt}
\lhead{Team Treehouse}
\rhead{SQL Reporting by Example Part 4 Notes}

\begin{document}
\title{SQL Reporting by Example Part 4 Notes}
\author{Team Treehouse}
\maketitle

\bigskip

\section{Busiest Teachers}

\bigskip

\section{Mini-Subject Teachers}

\bigskip

\section{Janis' Schedule}

\bigskip

\section{Least Popular Subject}

\bigskip

\section{Finding the Trouble Maker}

\bigskip

\section{Most Popular Teacher}

\bigskip

\section{Bus Troubles}

\bigskip

\section{Quiz 1}

\bigskip

\begin{enumerate}[1.]
    \item

    Please fill in the correct answer in each blank provided below.

    \bigskip

    Write a query to find out which managers have more than 5 people on their
    team. If you need to use a count, use 'COUNT(1)'.

    \bigskip

    SELECT MANAGERS.FIRST\_NAME, MANAGERS.LAST\_NAME

    FROM MANAGERS

    JOIN EMPLOYEES ON EMPLOYEES.MANAGER\_ID = MANAGERS.ID

    GROUP BY MANAGERS.ID \_\_\_;


    \bigskip

    \textbf{Answer:} HAVING COUNT(1) > 5

    \item

    The EMPLOYEES table has 267 rows and the JOBS table has 28 rows. How many
    rows does the following query return?

    SELECT $\ast$

    FROM EMPLOYEES

    LEFT OUTER JOIN JOBS ON EMPLOYEES.JOB\_ID = JOBS.ID;

    \bigskip

    \begin{enumerate}[A.]
        \item It could be anything from 0 to 267
        \item More than 267
        \item 267
        \item 0
    \end{enumerate}

    \bigskip

    \textbf{Answer:} C

    \item

    Which keyword is like a WHERE clause for a GROUP BY?

    \bigskip

    \begin{enumerate}[A.]
        \item WITH
        \item CONTAINING
        \item ALSO
        \item HAVING
    \end{enumerate}

    \bigskip

    \textbf{Answer:} D

    \item

    Common Table Expressions (CTE) let you refactor your queries into bite sized
    chunks. How do you create a CTE?

    \bigskip

    \begin{enumerate}[A.]
        \item WITH name AS { query }
        \item RESOLVE name AS { query }
        \item ALLOW name AS { query }
        \item TAKE name AS { query }
    \end{enumerate}

    \bigskip

    \textbf{Answer:} A

    \item

    In SQL you can subtract one result set from another using the EXCEPT keyword.

    \bigskip

    \begin{enumerate}[A.]
        \item True
        \item False
    \end{enumerate}

    \bigskip

    \textbf{Answer:} A

\end{enumerate}


\end{document}