\documentclass[12pt]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[utf]{kotex}
\usepackage{hyperref}
\usepackage{accents}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=1
}

\lstset{style=mystyle}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.4pt}
\lhead{CSC 343}
\rhead{Worksheet 14}

\begin{document}
\title{CSC343 Worksheet 14}
\maketitle

\begin{enumerate}[1.]
    \item \textbf{Exercise 4.1.1:} Design a database for a bank, including information
    about customers and their accounts. Information about a customer includes their
    name, address, phone, and Social Security number. Accounts have numbers,
    types (e.g., savings, checking) and balances. Also record the customer(s) who
    own an account. Draw the E/R diagram for this database. Be sure to include
    arrows where appropriate, to indicate the multiplicity of a relationship.

    \item \textbf{Exercise 4.1.2:} Modify your solution to Exercise 4.1.1 as follows:

    \bigskip

    \begin{enumerate}[a)]
        \item Change your diagram so an account can have only one customer.
        \item Further change your diagram so a customer can have only one account.
        \item Change your original diagram of Exercise 4.1.1 so that a customer can have a set of addresses (which are street-city-state triples) and a set of phones. Remember that we do not allow attributes to have nonprimitive types, such as sets, in the E/R model.
        \item Further modify your diagram so that customers can have a set of addresses, and at each address there is a set of phones.
    \end{enumerate}

    \item \textbf{Exercise 4.1.3:} Give an E/R diagram for a database recording information
    about teams, players, and their fans, including:

    \begin{enumerate}[1.]
        \item For each team, its name, its players, its team captain (one of its players), and the colors of its uniform.
        \item For each player, his/her name.
        \item For each fan, his/her name, favorite teams, favorite players, and favorite color.
    \end{enumerate}

    \bigskip

    Remember that a set of colors is not a suitable attribute type for teams. How can you get around this restriction?

\end{enumerate}

\end{document}