\documentclass[12pt]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[utf]{kotex}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=1
}

\lstset{style=mystyle}

\begin{document}
\title{CSC236 Assignment 1}
\author{Hyungmo Gu}
\maketitle

\section*{Question 1}
\begin{enumerate}[a.]
    \item

    Yes. We can prove $P(235)$ follows from $P(234)$.

    \bigskip

    \begin{mdframed}
        \underline{\textbf{Rough Work:}}

        Assume $P(234)$. That is, every bipartite graph on 234 vertices has no more
        than $\frac{234^2}{4}$ edges.

        \bigskip

        We need to prove $P(235)$ follows. That is, every bipartite graph on 235
        vertices has no more than $\frac{235^2}{4}$ edges.

        \begin{enumerate}[1.]
            \item Find the configuration where bipartite graph on 235 vertices form most number of edges in
            terms of bipartite graph on 234 vertices.

            \begin{mdframed}
            Let $b$ be the bipartite graph with 235 vertices where
            117 vertices are in one partition and 118 vertices in
            the other partition (Note this is the configuration where maximum number of edges form).

            \end{mdframed}

            \item Show that $\frac{235^2}{4}$ is the most number of edges bipartite graph on 235
            vertices could form.

            \begin{mdframed}
            The bipartite graph with 117 vertices on both sides of partition has
            $\frac{234^2}{4}$ edges, and the assumption tells us this is the maximum number of edges the
            bipartite graph could form.

            \bigskip

            Since we know $b$ has 117 more edges than the bipartite graph with 117 vertices on
            both sides, using these facts, we can conclude the upper bound number of edges for the bipartite
            graph with 235 vertices is

            \begin{align}
                \frac{234^2}{4} + 117 &= \frac{234^2}{4} + \frac{4 \cdot 117}{4}\\
                &= \frac{234^2 + 2 \cdot 234}{4}\\
                &\leq \frac{234^2 + 2 \cdot 234 + 1}{4}\\
                &= \frac{(234+1)^2}{4}\\
                &= \frac{(235)^2}{4}
            \end{align}

            \bigskip
            \end{mdframed}
        \end{enumerate}

    \end{mdframed}
\end{enumerate}

\section*{Question 2}

\section*{Question 3}

\section*{Question 4}

\end{document}