\documentclass[12pt]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[utf]{kotex}
\usepackage{hyperref}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=1
}

\lstset{style=mystyle}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.4pt}
\lhead{CSC 373}
\rhead{Worksheet 4}

\begin{document}
\title{CSC373 Worksheet 4}
\maketitle

\bigskip

Source: \href{http://www.cs.toronto.edu/~denisp/csc373/material.html}{link}

\bigskip

\begin{enumerate}[1.]
    \item \textbf{CLRS 22.1-1:} Given an adjacency-list representation of a directed graph, how long does it take
    to compute the out-degree of every vertex? How long does it take to compute the in-degrees?

    \item \textbf{CLRS 22.1-3:} The transpose of a directed graph $G = (V,E)$ is the graph $G^T = (V,E^T)$, where
    $E^T = \{(v,u) \in V \times V : (u,v) \in E\}$. Thus, $G^T$ is $G$ with all its edges reversed.
    Describe efficient algorithms for computing $G^T$ from $G$, for both the adjacencylist
    and adjacency-matrix representations of $G$. Analyze the running times of your
    algorithms.

    \item \textbf{CLRS 22.2-8:} The diameter of a tree $T = (V,E)$ is defined as $\text{max}_{u,v \in V} \delta(u,v)$, that is, the
    largest of all shortest-path distances in the tree. Give an efficient algorithm to
    compute the diameter of a tree, and analyze the running time of your algorithm.

    \item \textbf{CLRS 22.3-2:} Show how depth-first search works on the graph of Figure 22.6. Assume that the
    for loop of lines 5–7 of the DFS procedure considers the vertices in alphabetical
    order, and assume that each adjacency list is ordered alphabetically. Show the
    discovery and finishing times for each vertex, and show the classification of each
    edge.

    \item \textbf{CLRS 23.1-1:} Let $(u,v)$ be a minimum-weight edge in a connected graph $G$. Show that $(u,v)$
    belongs to some minimum spanning tree of $G$.

    \item \textbf{CLRS 23.2-2:} Suppose that we represent the graph $G = (V,E)$ as an adjacency matrix. Give a
    simple implementation of Prim’s algorithm for this case that runs in $\mathcal{O}(V^2)$ time.

    \item \textbf{CLRS 24.1-3:}
    Given a weighted, directed graph $G = (V,E)$ with no negative-weight cycles,
    let $m$ be the maximum over all vertices $v \in V$ of the minimum number of edges
    in a shortest path from the source $s$ to $v$. (Here, the shortest path is by weight, not
    the number of edges.) Suggest a simple change to the Bellman-Ford algorithm that
    allows it to terminate in $m + 1$ passes, even if $m$ is not known in advance.

    \item \textbf{CLRS 24.1-4:} Modify the Bellman-Ford algorithm so that it sets :d to 1 for all vertices  for
    which there is a negative-weight cycle on some path from the source to .

    \item \textbf{CLRS 24.3-6:} We are given a directed graph $G = (V,E)$ on which each edge $(u,v) \in E$ has an
    associated value $r(u,v)$, which is a real number in the range $0 \leq r(u,v) \leq 1$ that
    represents the reliability of a communication channel from vertex $u$ to vertex $v$.
    We interpret $r(u,v)$ as the probability that the channel from $u$ to $v$ will not fail,
    and we assume that these probabilities are independent. Give an efficient algorithm
    to find the most reliable path between two given vertices.

    \item \textbf{CLRS 25.2-6:} How can we use the output of the Floyd-Warshall algorithm to detect the presence
    of a negative-weight cycle?

    \item \textbf{CLRS 25.3-6:}
    Professor Michener claims that there is no need to create a new source vertex in
    line 1 of JOHNSON. He claims that instead we can just use $G' = G$ and let $s$ be any
    vertex. Give an example of a weighted, directed graph $G$ for which incorporating
    the professor’s idea into JOHNSON causes incorrect answers. Then show that if $G$
    is strongly connected (every vertex is reachable from every other vertex), the results
    returned by JOHNSON with the professor’s modification are correct.

\end{enumerate}

\end{document}