\documentclass[12pt]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdframed}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[utf]{kotex}
\usepackage{hyperref}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=1
}

\lstset{style=mystyle}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.4pt}
\lhead{Team Treehouse}
\rhead{SQL Basics Part 1 Notes}

\begin{document}
\title{SQL Basics Part 1 Notes}
\author{Team Treehouse}
\maketitle

\section{Why this Course?}

\bigskip

\section{Data is Everywhere}

\bigskip

\section{Talking to Databases with SQL}

\bigskip

\section{Organizing Data With Databases}

\bigskip

\section{Types of Data}

\bigskip

\section{Quiz 1}

\bigskip

\begin{enumerate}[1.]
    \item

    Which of these definitions bests suits the term database?

    \bigskip

    \begin{enumerate}[A.]
        \item A web server.
        \item All of the information stored on your computer.
        \item A spreadsheet application.
        \item A computerized system for the storage and retrieval of organized information.
    \end{enumerate}

    \bigskip

    \textbf{Answer:} D

    \item

    Please fill in the correct answer in each blank provided below.

    \bigskip

    The language you use to talk to databases is \_\_\_.

    \bigskip

    \textbf{Answer:} SQL

    \item

    Databases organize their information into structures called:

    \bigskip

    \begin{enumerate}[A.]
        \item Charts
        \item Multi-dimensional Arrays
        \item Spreadsheets
        \item Tables
    \end{enumerate}

    \bigskip

    \textbf{Answer:} D

    \item

    In a table, what are the vertical (top-to-bottom) structures called?

    \bigskip

    \begin{enumerate}[A.]
        \item Rows
        \item Columns
    \end{enumerate}

    \bigskip

    \textbf{Answer:} B

    \item

    Each entry in a table is known as a:

    \bigskip

    \begin{enumerate}[A.]
        \item Relation
        \item Data type
        \item Row
        \item Column
    \end{enumerate}

    \bigskip

    \textbf{Answer:} C

    \item

    A short description or bio would be best suited to which data type?

    \bigskip

    \begin{enumerate}[A.]
        \item Date
        \item Numeric
        \item Text
    \end{enumerate}

    \bigskip

    \textbf{Answer:} C

    \item

    What data type would best suit the prices of food on a menu?

    \bigskip

    \begin{enumerate}[A.]
        \item Date
        \item Text
        \item Numeric
    \end{enumerate}

    \bigskip

    \textbf{Answer:} C

    \item

    In an appointments table for a doctor's office, what would be the best data
    format to store the day of the appointment?

    \bigskip

    \begin{enumerate}[A.]
        \item Text
        \item Date
        \item Numeric
    \end{enumerate}

    \bigskip

    \textbf{Answer:} B
\end{enumerate}


\end{document}